WSClean: an implementation of a fast, generic wide-field imager for radio astronomy

### 2014-07-04 articles/2014/Article-WSClean/wsclean.tex
Fixing figures as requested by editor: adding quantity and units where necessary, making line widths correct in legends
Mention 3 author-papers in full in first mention

@@

There are several methods to deal with the $w$-term during imaging: faceting \citep{facetting-cornwell}; a three-dimensional Fourier transform \citep{perley-noncoplanar-arrays}; $w$-projection \citep{wprojection-cornwell}; $w$-stacking \citep{ska-memo-regridding-2011}; and warped snapshots \citep{perley-noncoplanar-arrays}. Hybrid methods are sometimes useful, such as with the $w$-snapshots method \citep{widefield-imaging-ska-cornwell}.

@@

\begin{figure*}%
\begin{subfigure}{.5\linewidth}%
\includegraphics[width=\linewidth]{img/benchmark-nsamples/nsamples}%
\caption{}\label{fig:timing-nsamples}%
\end{subfigure}%
\hspace{-.05\linewidth}\begin{subfigure}{.5\linewidth}%
\includegraphics[width=\linewidth]{img/benchmark-zenith-angle/za}%
\caption{}\label{fig:timing-zenith-angle}%
\end{subfigure}\\
\begin{subfigure}{.5\linewidth}%
\includegraphics[width=\linewidth]{img/benchmark-resolution/resolution}
\caption{}\label{fig:timing-resolution}%
\end{subfigure}%
\hspace{-.05\linewidth}\begin{subfigure}{.5\linewidth}%
\includegraphics[width=\linewidth]{img/benchmark-channels/channels}
\caption{}\label{fig:timing-channels}%
\end{subfigure}\\
\begin{subfigure}{.5\linewidth}%
\includegraphics[width=\linewidth]{img/benchmark-fov/fov}
\caption{}\label{fig:timing-fov}%
\end{subfigure}%
\caption{Imaging performance as a function of several parameters. Error bars show 5$\sigma$ level. Unfinished lines indicate the imager could not run the specific configuration successfully. The label ``R+\textsc{wsclean}'' refers to using WSClean with the recentring technique described in \S\ref{sec:snapshot-imaging-theory}.}\label{fig:timings}
\end{figure*}

>>>>

% By changing this definition from {} to {-bw}, the grayscale plots are used in Figure 7.
%\newcommand{\bwimgextension}{-bw}
\newcommand{\bwimgextension}{}

@@

There are several methods to deal with the $w$-term during imaging: faceting \citep{facetting-cornwell}; a three-dimensional Fourier transform \citep{perley-noncoplanar-arrays}; $w$-projection \citep*{wprojection-cornwell}; $w$-stacking \citep{ska-memo-regridding-2011}; and warped snapshots \citep{perley-noncoplanar-arrays}. Hybrid methods are sometimes useful, such as with the $w$-snapshots method \citep*{widefield-imaging-ska-cornwell}.

@@

\begin{figure*}%
\begin{subfigure}{.5\linewidth}%
\includegraphics[width=\linewidth]{img/benchmark-nsamples/nsamples\bwimgextension}%
\caption{}\label{fig:timing-nsamples}%
\end{subfigure}%
\hspace{-.05\linewidth}\begin{subfigure}{.5\linewidth}%
\includegraphics[width=\linewidth]{img/benchmark-zenith-angle/za\bwimgextension}%
\caption{}\label{fig:timing-zenith-angle}%
\end{subfigure}\\
\begin{subfigure}{.5\linewidth}%
\includegraphics[width=\linewidth]{img/benchmark-resolution/resolution\bwimgextension}
\caption{}\label{fig:timing-resolution}%
\end{subfigure}%
\hspace{-.05\linewidth}\begin{subfigure}{.5\linewidth}%
\includegraphics[width=\linewidth]{img/benchmark-channels/channels\bwimgextension}
\caption{}\label{fig:timing-channels}%
\end{subfigure}\\
\begin{subfigure}{.5\linewidth}%
\includegraphics[width=\linewidth]{img/benchmark-fov/fov\bwimgextension}
\caption{}\label{fig:timing-fov}%
\end{subfigure}%
\caption{Imaging performance as a function of several parameters. Error bars show 5$\sigma$ level. Unfinished lines indicate the imager could not run the specific configuration successfully. The label ``R+\textsc{wsclean}'' refers to using WSClean with the recentring technique described in \S\ref{sec:snapshot-imaging-theory}.}\label{fig:timings}
\end{figure*}
